---
title: "DAACS - STM Model Representative Essays"
author: 'Sean Connin'
date:: '05/17/22'
output:
  html_document: 
    toc: TRUE
    toc-title: ""
    toc_depth: 3
    toc_float: 
      collapsed: TRUE
      smooth_scroll: FALSE
    number_sections: true
    df_print: paged
    code_folding: hide
    theme: sandstone
    highlight: tango
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

load libraries

```{r}
library(tidyverse)
library(httr)
library(magrittr)
library(stm)
library(tidytext)
```

Load processed corpus and optimized stm models. The latter include models for prevalence and prevalence+content.

```{r}

#load processed corpus - documents, vocab, meta

processed<-load('processed_corpus_final.Rdata')

#load models

load('optimized.prevalence.models.6_32.Rda')   # e.g., optimized prevalence: stm.model.12

load('content.prevalence.models.6_32.Rda') # e.g.,     # optimized prevalence & content: content_prev.model.k12

# load prevalence & content models (stm())

basic.stm<-load('basic.stm.models.6_32.Rda')

```

Filter raw DAACS essays using the processed meta file doc_id & institution column identifiers. This will exclude essays removed as part of the filtering process.

```{r}

# subset doc_id, institution, and text from prepDocuments output

filtered<-meta%>%
  select(doc_id, institution, text)

#load raw data

preclean<-read_csv("preclean_text.csv")


# remove observations in original data that are not included in prepDocuments output -- for use in topic exemplar review

original<- inner_join(preclean, filtered, by=c('doc_id', 'institution'))%>%
  rename(text=text.x)

```


The following block includes a function to identify passages (using findThoughts) that exemplify the topic(s) in the processed text of documents for a given model. Creates a directory to store the results. 

_The following code needs to be altered for each model of interest._

Arguments of interest:

thresh: Sets a minimum threshold for the estimated topic proportion for displayed documents. It defaults to imposing no restrictions.

n: number of docs to display


```{r warning=FALSE}

# build function to generate exemplar essays for each prevalence model (top 5)

exemplars<-function(model, number, topic){
  
# create folder to store files
  
  mainDir<-getwd() #set working directory
  
  fname <- 'Essay_Passages'  # folder to create in wd
  
  dir.create(file.path(mainDir, fname), showWarnings = FALSE) # create the folder as a subdirectory
  
  dir.create(file.path(mainDir, fname, paste0('Passages_stm.model', number)), showWarnings = FALSE)
  
  setwd(file.path(mainDir, fname, paste0('Passages_stm.model', number))) #set temporary working directory
  
  for(i in seq_along(topic)){
  
    png(paste0('Topic',i, '.png')) # create file names for plots 
    
    name <-findThoughts(model, texts = original$text, topics = i, n=5)$docs[[1]] # this returns preclean text
    index<-findThoughts(model, texts = original$text, topics = i, n=5)$index[[1]] # this returns index # for the texts, access via return()/slice()
    examples<-plotQuote(name, width=100, maxwidth=500, text.cex=1,
    main = paste0('stm.model.',number,': Topic ', i))
    
    dev.off() # close save plot
    
    
  }
  
}

exemplars(stm.model12, 12, c(1:12)) # number is our model number, topic is list of topics

```

Repeat this process for content & prevalence to determine if there are any differences

Note: there are differences that may be due to initialization starting points. 

```{r warning=FALSE, fig.width=25}

# build function to generate exemplar essays for each prevalence model model (top 5)

exemplars<-function(model, number, topic){
  
# create folder to store files
  
  mainDir<-getwd() #set working directory
  
  fname <- 'Passages-Prev&Content'  # folder to create in wd
  
  dir.create(file.path(mainDir, fname), showWarnings = FALSE) # create the folder as a subdirectory
  
  dir.create(file.path(mainDir, fname, paste0('Passages_Con.Prev.Model', number)), showWarnings = FALSE)
  
  setwd(file.path(mainDir, fname, paste0('Passages_Con.Prev.Model', number))) #set temporary working directory
  
  for(i in seq_along(topic)){
  
    png(paste0('Topic',i, '.png')) # create file names for plots 
    
    name <-findThoughts(model, texts = original$text, topics = i, n=4)$docs[[1]] # this returns preclean text
    index<-findThoughts(model, texts = original$text, topics = i, n=4)$index[[1]] # this returns index # for the texts, access via return()/slice()
    examples<-plotQuote(name, width=100, maxwidth=500, text.cex=.7,
    main = paste0('stm.model.',number,': Topic ', i))
    
    dev.off() # close save plot
    
    
  }
  
}


exemplars(content_prev.model.k6$runout[[1]], 6, c(1:6)) # number is our model number, topic is list of topics
```

Finally, extract passages using the basic stm models. The resulting files will be used for downstream analyses and writeup.

```{r warning = FALSE}

# build function to generate exemplar essays for stm basic model (top 5)

exemplars<-function(model, number, topic){
  
# create folder to store files
  
  mainDir<-getwd() #set working directory
  
  fname <- 'Passages-basic.stm'  # folder to create in wd
  
  dir.create(file.path(mainDir, fname), showWarnings = FALSE) # create the folder as a subdirectory
  
  dir.create(file.path(mainDir, fname, paste0('Passages_basic.stm.Model', number)), showWarnings = FALSE)
  
  setwd(file.path(mainDir, fname, paste0('Passages_basic.stm.Model', number))) #set temporary working directory
  
  for(i in seq_along(topic)){
  
    png(paste0('Topic',i, '.png')) # create file names for plots 
    
    name <-findThoughts(model, texts = original$text, topics = i, n=4)$docs[[1]] # this returns preclean text
    index<-findThoughts(model, texts = original$text, topics = i, n=4)$index[[1]] # this returns index # for the texts, access via return()/slice()
    examples<-plotQuote(name, width=100, maxwidth=500, text.cex=.7,
    main = paste0('stm.model.',number,': Topic ', i))
    
    dev.off() # close save plot
    
    
  }
  
}


exemplars(stm.model.k32, 32, c(1:32)) # number is our model number, topic is list of topics

```

Write top 5 representative essays (raw data) by model and topic to file. Note, the essays extracted here come from the basic stm models - which include prevalence and content formula. The decision to use this set of files owes to results and downstream analyses described in the file analyses6_32.

```{r warning=FALSE}


#create document table with and meta variables for stm_18

identifiers<- meta%>%select(doc_id, institution)

# build function to generate original essays for each topic (top 5)

top.essays<-function(model, K, id, topic, raw.data){
  
# create folder to store files
  
  mainDir<-getwd() #set working directory
  
  fname <- 'Top Essays'  # folder to create in wd
  
  dir.create(file.path(mainDir, fname), showWarnings = FALSE) # create the folder as a subdirectory
  
  dir.create(file.path(mainDir, fname, paste0('Essays.Model', K)), showWarnings = FALSE)
  
  setwd(file.path(mainDir, fname, paste0('Essays.Model', K))) #set temporary working directory
  
  table <- make.dt(model, meta = id)%>%  # table with document proportions
    relocate(c(doc_id, institution), .after=docnum)
  
  for(i in seq_along(topic)){
    
    topic.pointer<-paste0('Topic', i) # update topic number
    
    subset<-table%>%
      select(doc_id, institution, topic.pointer)
    
    top5<-subset[order(-subset[,3]),]%>%  # arrange subset by topic col, could not get this to work with dplyr arrange without hardcoding col name
      slice(1:5)
    
    raw.essays<-inner_join(raw.data, top5, by = c('doc_id', 'institution'))%>%
      select(text)%>%
      table()
    
    essay.filename<- paste0('topic', i,'essays.txt')
    
    write.table(raw.essays, file = essay.filename, sep = "\t", row.names = FALSE, col.names = FALSE)
  }
  
}

# write top 5 representative essays for each model and topic to file

top.essays(stm.model.k6, 6, identifiers, c(1:6), original)
top.essays(stm.model.k12, 12, identifiers, c(1:12), original)
top.essays(stm.model.k18, 18, identifiers, c(1:18), original)
top.essays(stm.model.k24, 24, identifiers, c(1:24), original)
top.essays(stm.model.k32, 32, identifiers, c(1:32), original)

```
