---
title: "DAACS - STM Model Representative Essays"
author: 'Sean Connin'
date: "05/17/22"
output:
  html_document: 
    toc: TRUE
    toc-title: ""
    toc_depth: 3
    toc_float: 
      collapsed: TRUE
      smooth_scroll: FALSE
    number_sections: true
    df_print: paged
    code_folding: hide
    theme: sandstone
    highlight: tango
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

load libraries

```{r}
library(tidyverse)
library(magrittr)
library(stm)
library(tidytext)

# Shared helpers: write_topic_exemplars(), write_top_essays()
source("R/exemplars.R")
```

`httr` was dropped from this block -- declared here and in two other notebooks,
never called (`CODE_REVIEW.md` S4).

Load processed corpus and optimized stm models. The latter include models for prevalence and prevalence+content.

```{r}
# load processed corpus - documents, vocab, meta

processed <- load("processed_corpus_final.Rdata")

# load models

load("optimized.prevalence.models.6_32.Rda") # e.g., optimized prevalence: stm.model.12

load("optimized.prevalence.content.models.6_32.Rda") # e.g.,     # optimized prevalence & content: content_prev.model.k12

# load prevalence & content models (stm())

basic.stm <- load("stm.prevalence.content.models.6_32.Rda")
```

Filter raw DAACS essays using the processed meta file doc_id & institution column identifiers. This will exclude essays removed as part of the filtering process.

```{r}
# subset doc_id, institution, and text from prepDocuments output

filtered <- meta %>%
  select(doc_id, institution, text)

# load raw data

preclean <- read_csv("preclean_text.csv")


# remove observations in original data that are not included in prepDocuments output -- for use in topic exemplar review

original <- inner_join(preclean, filtered, by = c("doc_id", "institution")) %>%
  rename(text = text.x)
```


These blocks previously defined `exemplars()` three times over, differing only in
output folder, number of documents shown, and text size, plus a fourth
`top.essays()` sharing the same scaffolding. All four are now one pair of
helpers in `R/exemplars.R`, which fixes three defects once instead of three
times:

- **`setwd()` with no restore.** Each copy changed the working directory and
  never changed it back, so every later chunk ran somewhere else and an error
  mid-loop stranded the session in a subdirectory. Paths are now built with
  `file.path()`; no directory change happens at all.
- **`for (i in seq_along(topic))`** used a *position* where a *topic number* was
  meant. Correct only because every caller passed `1:K` -- `exemplars(model, 6,
  c(3, 7))` would have rendered topics 1 and 2 while labelling them "Topic 1"
  and "Topic 2".
- **`findThoughts()` called twice per topic** with identical arguments, the
  second result discarded. Half the work was wasted.

`write_top_essays()` also changes what it writes. The original piped essays
through `base::table()` before `write.table()`, which counted occurrences of
each distinct essay -- always 1, since essays are unique -- and emitted
`"essay text"\t1` per line. It now writes the essay text plainly, which is
evidently what was intended. See `CODE_REVIEW.md`.

```{r warning=FALSE}
# Optimized prevalence model (manyTopics)
write_topic_exemplars(
  stm.model.12,
  model_label = "stm.model.12",
  topics = 1:12,
  texts = original$text,
  collection = "Essay_Passages",
  n = 5,
  text_cex = 1
)
```

Repeat for prevalence & content, to see whether the exemplars differ. Note there
are differences, which may owe to different initialization starting points.

```{r warning=FALSE}
write_topic_exemplars(
  content_prev.model.k6$runout[[1]],
  model_label = "content_prev.model.k6",
  topics = 1:6,
  texts = original$text,
  collection = "Passages-Prev&Content",
  n = 4,
  text_cex = 0.7
)
```

Finally, extract passages from the basic stm models. These files are used for
downstream analyses and writeup.

```{r warning=FALSE}
write_topic_exemplars(
  stm.pc.32,
  model_label = "stm.pc.32",
  topics = 1:32,
  texts = original$text,
  collection = "Passages-basic.stm",
  n = 4,
  text_cex = 0.7
)
```

Write the top 5 representative essays (raw text) per model and topic to file.
These come from the basic stm models, which include prevalence and content
formulas -- see the results discussed in stm_analyses_final.

```{r warning=FALSE}
identifiers <- meta %>% select(doc_id, institution)

topic_tables <- list(
  "stm.pc.6" = make.dt(stm.pc.6, meta = identifiers),
  "stm.pc.12" = make.dt(stm.pc.12, meta = identifiers),
  "stm.pc.18" = make.dt(stm.pc.18, meta = identifiers),
  "stm.pc.24" = make.dt(stm.pc.24, meta = identifiers),
  "stm.pc.32" = make.dt(stm.pc.32, meta = identifiers)
)

for (label in names(topic_tables)) {
  k <- as.integer(sub("stm[.]pc[.]", "", label))
  write_top_essays(
    topic_table = topic_tables[[label]],
    topics = seq_len(k),
    raw_data = original,
    model_label = label,
    collection = "Top Essays",
    n = 5
  )
}
```
