---
title: "DAACS - STM Model Representative Essays"
author: 'Sean Connin'
date: "05/17/22"
output:
  html_document: 
    toc: TRUE
    toc-title: ""
    toc_depth: 3
    toc_float: 
      collapsed: TRUE
      smooth_scroll: FALSE
    number_sections: true
    df_print: paged
    code_folding: hide
    theme: sandstone
    highlight: tango
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

load libraries

```{r}
# The tidyverse core, loaded explicitly rather than through the umbrella
# package. `library(tidyverse)` also pulls in `ragg`, which needs the
# harfbuzz/fribidi system libraries -- a build dependency this analysis never
# uses, and one that makes the project fail to install on a clean machine.
# These are the same namespaces `library(tidyverse)` attaches, minus
# `lubridate` (no date handling anywhere in the pipeline).
library(dplyr)
library(ggplot2)
library(tibble)
library(tidyr)
library(readr)
library(purrr)
library(stringr)
library(forcats)
library(magrittr)
library(stm)
library(tidytext)

# Shared helpers: write_topic_exemplars(), write_top_essays()
source("R/exemplars.R")
```

`httr` was dropped from this block -- declared here and in two other notebooks,
never called (`CODE_REVIEW.md` S4).

Load processed corpus and optimized stm models. The latter include models for prevalence and prevalence+content.

```{r}
# load processed corpus - documents, vocab, meta

processed <- load("processed_corpus_final.Rdata")

# load models -- all five specifications at K = 12

load("optimized.prevalence.model.k12.Rda") # stm.model.12          (manyTopics)
load("optimized.prevalence.content.model.k12.Rda") # content_prev.model.k12 (selectModel)
load("stm.prevalence.content.model.k12.Rda") # stm.pc.12             (stm, prev + content)
load("stm.prevalence.model.k12.Rda") # stm.p.12              (stm, prevalence)
load("stm.content.model.k12.Rda") # stm.c.12              (stm, content)
```

**K = 12 only.** This notebook previously produced exemplars at K = 6 and K = 32 and top-essay files
across all five values of K. That material was the *input* to the model-review process that settled
on K = 12; that review is complete, so it is no longer regenerated. The five models below differ in
specification, not in topic count, which is the comparison that remains useful. See `CODE_REVIEW.md`.

Filter raw DAACS essays using the processed meta file doc_id & institution column identifiers. This will exclude essays removed as part of the filtering process.

```{r}
# subset doc_id, institution, and text from prepDocuments output

filtered <- meta %>%
  select(doc_id, institution, text)

# load raw data

preclean <- read_csv("preclean_text.csv")


# remove observations in original data that are not included in prepDocuments output -- for use in topic exemplar review

original <- inner_join(preclean, filtered, by = c("doc_id", "institution")) %>%
  rename(text = text.x)
```


These blocks previously defined `exemplars()` three times over, differing only in
output folder, number of documents shown, and text size, plus a fourth
`top.essays()` sharing the same scaffolding. All four are now one pair of
helpers in `R/exemplars.R`, which fixes three defects once instead of three
times:

- **`setwd()` with no restore.** Each copy changed the working directory and
  never changed it back, so every later chunk ran somewhere else and an error
  mid-loop stranded the session in a subdirectory. Paths are now built with
  `file.path()`; no directory change happens at all.
- **`for (i in seq_along(topic))`** used a *position* where a *topic number* was
  meant. Correct only because every caller passed `1:K` -- `exemplars(model, 6,
  c(3, 7))` would have rendered topics 1 and 2 while labelling them "Topic 1"
  and "Topic 2".
- **`findThoughts()` called twice per topic** with identical arguments, the
  second result discarded. Half the work was wasted.

`write_top_essays()` also changes what it writes. The original piped essays
through `base::table()` before `write.table()`, which counted occurrences of
each distinct essay -- always 1, since essays are unique -- and emitted
`"essay text"\t1` per line. It now writes the essay text plainly, which is
evidently what was intended. See `CODE_REVIEW.md`.

Exemplar passages for each of the five K = 12 specifications. Differences
between them reflect the model formula and initialization, not the topic count.

```{r warning=FALSE}
k12_models <- list(
  "stm.model.12" = stm.model.12, # manyTopics, prevalence
  "content_prev.model.k12" = content_prev.model.k12$runout[[1]], # selectModel, prev + content
  "stm.pc.12" = stm.pc.12, # stm, prevalence + content
  "stm.p.12" = stm.p.12, # stm, prevalence
  "stm.c.12" = stm.c.12 # stm, content
)

for (label in names(k12_models)) {
  write_topic_exemplars(
    k12_models[[label]],
    model_label = label,
    topics = 1:12,
    texts = original$text,
    collection = "Essay_Passages",
    n = 5,
    text_cex = 1
  )
}
```

Write the top 5 representative essays (raw text) per model and topic to file,
for the same five K = 12 specifications.

```{r warning=FALSE}
identifiers <- meta %>% select(doc_id, institution)

for (label in names(k12_models)) {
  write_top_essays(
    topic_table = make.dt(k12_models[[label]], meta = identifiers),
    topics = 1:12,
    raw_data = original,
    model_label = label,
    collection = "Top Essays",
    n = 5
  )
}
```
