---
title: "DAACS - STM Random Forest"
author: "Sean Connin"
date: "05/27/22"
output:
  html_document: 
    toc: TRUE
    toc-title: ""
    toc_depth: 3
    toc_float: 
      collapsed: TRUE
      smooth_scroll: FALSE
    number_sections: true
    df_print: paged
    code_folding: hide
    theme: sandstone
    highlight: tango
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
# The tidyverse core, loaded explicitly rather than through the umbrella
# package. `library(tidyverse)` also pulls in `ragg`, which needs the
# harfbuzz/fribidi system libraries -- a build dependency this analysis never
# uses, and one that makes the project fail to install on a clean machine.
# These are the same namespaces `library(tidyverse)` attaches, minus
# `lubridate` (no date handling anywhere in the pipeline).
library(dplyr)
library(ggplot2)
library(tibble)
library(tidyr)
library(readr)
library(purrr)
library(stringr)
library(forcats)
library(janitor)
library(magrittr)
library(stm)
library(randomForest)

# Shared helpers
source("R/rf_topic_importance.R") # fit_topic_forests(), plot_topic_importance()
source("R/topic_labels.R") # topic_labels(), topic_rename_map()
```

Two libraries were dropped here. `tuneR` is an audio-processing package that
nothing in this file calls -- almost certainly a mistaken autocomplete for `tune`.
`vip` has been archived from CRAN, so `install.packages("vip")` now fails; its
variable-importance plots are reproduced with ggplot2 in `R/rf_topic_importance.R`,
reading the same `randomForest::importance()` values it read.

This is an initial inferential exploration of topic proportions and srl component scores/feedback views using Random Forest.

First, load stm prevalence models for analysis 

```{r}
# load basic stm prevalence model

load("stm.prevalence.models.6_32.Rda")

# disaggregate models

stm.p.6
stm.p.12
stm.p.18
stm.p.24
stm.p.32
```
load raw daacs data and subset srl variables

```{r}
# load raw datasets

wgu_data <- load(file = "DAACS-WGU.rda")
ec_data <- load(file = "DAACS-EC.rda")
alb_data <- load(file = "DAACS-ualbany.rda")

# subset srl features from daacs datasets

wgu.srl <- daacs.wgu %>%
  select(DAACS_ID, srl_grit, srl_strategies, srl_motivation, srl_metacognition, srl_managing_time, srl_managing_environment, srl_anxiety, srl_mindset, srl_self_efficacy, srl_evaluation, srl_planning, srl_help_seeking, srl_understanding, srl_mastery_orientation) %>%
  rename(doc_id = DAACS_ID) %>%
  mutate(institution = "WG") %>%
  relocate(institution, .after = doc_id) %>%
  filter(!is.na(srl_strategies))

ec.srl <- daacs.ec %>%
  select(DAACS_ID, srl_grit, srl_strategies, srl_motivation, srl_metacognition, srl_managing_time, srl_managing_environment, srl_anxiety, srl_mindset, srl_self_efficacy, srl_evaluation, srl_planning, srl_help_seeking, srl_understanding, srl_mastery_orientation) %>%
  rename(doc_id = DAACS_ID) %>%
  mutate(institution = "EC") %>%
  relocate(institution, .after = doc_id) %>%
  filter(!is.na(srl_strategies))

alb.srl <- daacs.ualbany %>%
  select(DAACS_ID, srl_grit, srl_strategies, srl_motivation, srl_metacognition, srl_managing_time, srl_managing_environment, srl_anxiety, srl_mindset, srl_self_efficacy, srl_evaluation, srl_planning, srl_help_seeking, srl_understanding, srl_mastery_orientation) %>%
  rename(doc_id = DAACS_ID) %>%
  # Albany collects no grit measure: 3,941 rows, 0 non-NA, 490 NaN. Stated
  # directly rather than through a case_when() that appears to transform
  # something. The previous line -- case_when(srl_grit %in% NaN ~ NA) -- had no
  # fallback branch and used `%in% NaN`, which never matches because NaN does
  # not compare equal to itself. It destroyed nothing only because the column
  # was already empty; it would have emptied it the moment data arrived.
  # See CODE_REVIEW.md S1-1.
  mutate(srl_grit = NA_real_) %>%
  mutate(institution = "Alb") %>%
  relocate(institution, .after = doc_id) %>%
  filter(!is.na(srl_strategies))

# create single dataframe for srl features

srl.features <- rbind(wgu.srl, ec.srl, alb.srl)

srl.features %<>%
  mutate(across(where(is.numeric), \(x) round(x, 2)))
```

load processed corpus

```{r}
# load processed corpus - documents, vocab, meta

processed <- load("processed_corpus_final.Rdata")
```

Build topic proportion tables

```{r}
# subset doc_id and institution from meta file --> identifiers

table.meta <- meta %>%
  select(doc_id, institution)

# create topic prevalence tables that includes identifiers
t.6 <- make.dt(stm.p.6, meta = table.meta) %>%
  relocate(c(doc_id, institution), .after = docnum) %>%
  select(!docnum)
t.12 <- make.dt(stm.p.12, meta = table.meta) %>%
  relocate(c(doc_id, institution), .after = docnum) %>%
  select(!docnum)
t.18 <- make.dt(stm.p.18, meta = table.meta) %>%
  relocate(c(doc_id, institution), .after = docnum) %>%
  select(!docnum)
t.24 <- make.dt(stm.p.24, meta = table.meta) %>%
  relocate(c(doc_id, institution), .after = docnum) %>%
  select(!docnum)
t.32 <- make.dt(stm.p.32, meta = table.meta) %>%
  relocate(c(doc_id, institution), .after = docnum) %>%
  select(!docnum)
```

Combine topic proportion and srl variables

```{r}
# combine topic data and srl covariate data into single dataframe

srl.topics.6 <- left_join(srl.features, t.6, by = c("doc_id", "institution"))
srl.topics.12 <- left_join(srl.features, t.12, by = c("doc_id", "institution"))
srl.topics.18 <- left_join(srl.features, t.18, by = c("doc_id", "institution"))
srl.topics.24 <- left_join(srl.features, t.24, by = c("doc_id", "institution"))
srl.topics.32 <- left_join(srl.features, t.32, by = c("doc_id", "institution"))
```

Build Random Forest models for the K=12 topics, assessing how much variance in
each topic's document prevalence is explained by the SRL component scores.

This replaces twelve near-identical fitting blocks and twelve `vip()` calls. Two
changes here alter reported numbers, and both are deliberate:

- **Every topic now reads `srl.topics.12`.** The previous topic-2 block read
  `srl.topics.32`, so its result described a different latent topic than its
  label claimed (`CODE_REVIEW.md` S1-2). Iterating makes that error impossible
  rather than merely corrected.
- **Fitting is seeded.** The previous code called `randomForest()` with no
  `set.seed()`, so its figures could not be regenerated (S3-2). Several were
  near zero or negative, where the sign itself is not stable run to run.

Variance explained is returned as data rather than recorded in trailing
comments, so it can be sorted, plotted and compared against a re-run (S3-4).

```{r}
topic_forests <- fit_topic_forests(srl.topics.12, topics = 1:12, ntree = 1000)

topic_forests %>%
  select(topic, n_obs, var_explained) %>%
  arrange(desc(var_explained))
```

Variable importance for each topic. `plot_topic_importance()` reads the same
`randomForest::importance()` values `vip()` did.

```{r fig.width = 12, fig.height = 14}
importance_plots <- purrr::map2(
  topic_forests$model,
  topic_forests$topic,
  ~ plot_topic_importance(.x, title = paste("Topic", .y))
)

patchwork::wrap_plots(importance_plots, ncol = 3)
```
Construct dataframes that include Feedback Views (WGU)

```{r}
wgu.views <- daacs.wgu %>%
  clean_names() %>%
  select(daacs_id, feedback_views) %>%
  rename(doc_id = daacs_id) %>%
  mutate(institution = "WG") %>%
  relocate(institution, .after = doc_id) %>%
  filter(!is.na(feedback_views))


feedback.views.12 <- left_join(wgu.views, t.12, by = c("doc_id", "institution"))
```

The `.18`, `.24` and `.32` variants were removed rather than repaired
(`CODE_REVIEW.md` S1-3). All three joined `t.12`, so they were byte-identical
copies of `feedback.views.12` carrying labels that claimed otherwise, and
nothing downstream consumed them. Deleting mislabeled dead objects changes no
result; recreate them against `t.18`/`t.24`/`t.32` if those K values are ever
actually wanted.

Model feedback views as a response using topics as predictors. Approx 9.5 - 10% of variance explained.

```{r}
# Build dataframe for analysis

views12 <- feedback.views.12 %>%
  select(feedback_views, starts_with("topic")) %>%
  na.omit()

# rename columns

views12 %<>%
  rename(all_of(topic_rename_map()))

# clean names

views12 %<>% clean_names()

# build random forest model

set.seed(20220527)
views.model12 <- randomForest(feedback_views ~ ., data = views12, ntree = 1000, importance = TRUE)

cat("variance explained:", round(max(views.model12$rsq) * 100, 2), "%\n")

# plot variable importance based on model results

plot_topic_importance(
  views.model12,
  n_features = 12,
  title = "Feedback views: topic importance"
)
```

