---
title: "DAACS - STM ANALYSES"
author: "Sean Connin"
date: "05/27/22"
output:
  html_document: 
    toc: TRUE
    toc-title: ""
    toc_depth: 3
    toc_float: 
      collapsed: TRUE
      smooth_scroll: FALSE
    number_sections: true
    df_print: paged
    code_folding: hide
    theme: sandstone
    highlight: tango
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

load libraries

```{r}
# The tidyverse core, loaded explicitly rather than through the umbrella
# package. `library(tidyverse)` also pulls in `ragg`, which needs the
# harfbuzz/fribidi system libraries -- a build dependency this analysis never
# uses, and one that makes the project fail to install on a clean machine.
# These are the same namespaces `library(tidyverse)` attaches, minus
# `lubridate` (no date handling anywhere in the pipeline).
library(dplyr)
library(ggplot2)
library(tibble)
library(tidyr)
library(readr)
library(purrr)
library(stringr)
library(forcats)
library(magrittr)
library(stm)
library(igraph) # network graph
library(huge) # network graph
library(tidytext)
library(patchwork)
library(kableExtra)

# Shared helpers: TOPIC_LABELS_K12, topic_labels()
source("R/topic_labels.R")
```

`httr` was dropped from this block -- it was declared here and in two other
notebooks but never called (`CODE_REVIEW.md` S4).

Load corpus, kresult, and models -- from preprocess_data_final and stm topic models

Models loaded in this file. Each file is written by stm_models_final.Rmd; the object names below are
what `load()` restores into the global environment, so they are the names to reference downstream.

| File | Object | Fitted by | Formula |
|---|---|---|---|
| optimized.prevalence.model.k12.Rda | `stm.model.12` | `manyTopics()` | prevalence |
| optimized.prevalence.content.model.k12.Rda | `content_prev.model.k12` | `selectModel()` | prevalence + content |
| stm.prevalence.content.model.k12.Rda | `stm.pc.12` | `stm()` | prevalence + content |
| stm.prevalence.model.k12.Rda | `stm.p.12` | `stm()` | prevalence |
| stm.content.model.k12.Rda | `stm.c.12` | `stm()` | content |

Note: "optimized" refers to automatic selection based on high-likelihood values. The `selectModel()`
families return a list, so those objects are indexed as `$runout[[n]]` rather than used directly.

**K = 12 only.** These five models differ in specification, not in topic count. K was settled by
professional review of the clustering results across candidate models rather than by exclusivity and
coherence, and that review is complete — so `stm_models_final.rmd` no longer re-fits K = 6/18/24/32.
Every analysis in this file already referenced K = 12 exclusively; the one exception was the
exclusivity-vs-coherence comparison below, which is now inert. See `CODE_REVIEW.md`.

```{r}
# load processed corpus - documents, vocab, meta

processed <- load("processed_corpus_final.Rdata")

# load optimized prevalence models

prev.models <- load("optimized.prevalence.model.k12.Rda")

# load optimized prevalence & content models

prev.content.models <- load("optimized.prevalence.content.model.k12.Rda")

# load basic stm prevalence & content models

prev.content.stm <- load("stm.prevalence.content.model.k12.Rda")

# load basic stm prevalence model

prev.stm <- load("stm.prevalence.model.k12.Rda")

# load basic stm content model

content.stm <- load("stm.content.model.k12.Rda")
```

Load raw essays and bind to filtered identifiers (doc_id, institution) - original text less any essays filtered out during preprocessing. 

```{r}
# subset doc_id and text from prepDocuments output

filtered <- meta %>%
  select(doc_id, institution, text)

filter_id <- filtered %>%
  select(doc_id)

# load raw data

preclean <- read_csv("preclean_text.csv")


# remove obs in original data that are not included in prepDocuments output -- for use in topic exemplar review

original <- left_join(filter_id, preclean, by = "doc_id")
```

## Exclusivity vs. coherence across K — not run

This was the one section of this file that required the full K sweep. It is retained as a record of
the diagnostic that was computed, but **it is not part of how K was chosen**: the selection was made
by professional review of the clustering results across candidate models, not by these two measures.
Since `stm_models_final.rmd` now fits K = 12 only, `stm.model.6/18/24/32` do not exist and this code
would error.

To restore it, un-comment the K sweep in `stm_models_final.rmd` and this chunk together — they are a
pair. The chunk is marked `eval = FALSE` so the notebook knits without it.

These plots cannot be graphed when a content formula is included.

```{r eval = FALSE}
# build dataframes with exclusivity and coherence measures for each optimized model

CE6 <- as.data.frame(cbind(c(1:6), exclusivity(stm.model.6), semanticCoherence(model = stm.model.6, documents), "Mod6"))
CE12 <- as.data.frame(cbind(c(1:12), exclusivity(stm.model.12), semanticCoherence(model = stm.model.12, documents), "Mod12"))
CE18 <- as.data.frame(cbind(c(1:18), exclusivity(stm.model.18), semanticCoherence(model = stm.model.18, documents), "Mod18"))
CE24 <- as.data.frame(cbind(c(1:24), exclusivity(stm.model.24), semanticCoherence(model = stm.model.24, documents), "Mod24"))
CE32 <- as.data.frame(cbind(c(1:32), exclusivity(stm.model.32), semanticCoherence(model = stm.model.32, documents), "Mod32"))

# combine diagnostics for each model

CE6_32 <- rbind(CE6, CE12, CE18, CE24, CE32)

# reset column names

colnames(CE6_32) <- c("K", "Exclusivity", "SemanticCoherence", "Model")

# reset feature types

CE6_32$Exclusivity <- as.numeric(as.character(CE6_32$Exclusivity))
CE6_32$SemanticCoherence <- as.numeric(as.character(CE6_32$SemanticCoherence))

CE6_32$Model <- factor(CE6_32$Model, levels = c("Mod6", "Mod12", "Mod18", "Mod24", "Mod32"))

# save(CE6_32, file="exclusivity_coherence6-28.Rdata")

# build exclusivity & coherence plot for models

plot <- ggplot(CE6_32, aes(SemanticCoherence, Exclusivity, color = Model)) +
  geom_point(size = 2, alpha = 0.7) +
  geom_text(aes(label = K), nudge_x = .09, nudge_y = .09, size = 2.5) +
  labs(
    x = "Semantic coherence",
    y = "Exclusivity",
    title = "Model Diagnostics: Exclusivity and Semantic Coherence",
    subtitle = "Prevalence Formula: manyTopics()"
  ) +
  theme_classic()
```






Plot topic quality  and prevalence for K = 12, prevalence model and basic STM. Highest probability words.

```{r}
# Plot topic quality by model (coherence & exclusivity)

topicQuality(stm.model.12, documents)
```

Compare topic prevalence across optimized and non-optimized models for K=12

```{r}
# plot topic prevalence across documents

plot(stm.model.12, main = "Topic Prevalence - K12 (manyTopics)") # highest probability words

# plot topic prevalence basic stm model

plot(stm.p.12, main = "Topic Prevalence - K12 (STM)")
```
It is possible to create a topic prevalence plot using models built on prevalence & content formula. This was not possible with the topicQuality() function. In this context, we can compare differencesin models (with same K) that pass the optimization process.

Note that the results will also be different from the optimized model built on prevalence formula alone, owing to different initializations and model selection. 

```{r}
# Each document's topic proportions sum to 1, so summing gamma across documents
# and dividing by the document count gives the mean proportion per topic.
#
# Two corrections here (CODE_REVIEW.md S1-4, S1-5), both of which change every
# proportion these five blocks plot:
#
#   - The divisor was hard-coded as 8120. The corpus holds 8210 documents --
#     the same digits transposed. It is now derived, and asserted against the
#     value recorded when the corpus was built.
#   - The sum was written `sum(., is.na(.), 0)`. sum() is variadic, so that
#     added the COUNT OF NAs to the total rather than removing them.
n_documents <- length(documents)
stopifnot(n_documents == 8210)

# plot k = 12, optimized prevalence formula

multi.p.12 <- tidy(stm.model.12, matrix = "gamma") %>%
  group_by(topic) %>%
  summarise(gamma = sum(gamma, na.rm = TRUE), .groups = "drop") %>%
  mutate(proportion = (gamma / n_documents) * 100)

multi.p.12$topic <- factor(multi.p.12$topic, levels = multi.p.12[order(multi.p.12$proportion, decreasing = FALSE), ]$topic)

m1 <- multi.p.12 %>% ggplot(aes(x = topic, y = proportion, fill = proportion)) +
  geom_col(alpha = 0.8, show.legend = FALSE) +
  labs(title = "Topic Prevalence within Corpus: K = 12", subtitle = "Topic Prevalence: manyTopics()", y = "Proportion (%)", x = "Topic") +
  coord_flip() +
  theme_classic()

# plot k = 12, prevalence & content: optimized model = 1

select.pc.12.1 <- tidy(content_prev.model.k12$runout[[1]], matrix = "gamma") %>%
  group_by(topic) %>%
  summarise(gamma = sum(gamma, na.rm = TRUE), .groups = "drop") %>%
  mutate(proportion = (gamma / n_documents) * 100)

select.pc.12.1$topic <- factor(select.pc.12.1$topic, levels = select.pc.12.1[order(select.pc.12.1$proportion, decreasing = FALSE), ]$topic)

m2 <- select.pc.12.1 %>% ggplot(aes(x = topic, y = proportion, fill = proportion)) +
  geom_col(alpha = 0.8, show.legend = FALSE) +
  labs(title = "Topic Prevalence: K = 12, Model 1", subtitle = "Prevalence & Content: selectModel()", y = "Proportion (%)", x = "Topic") +
  coord_flip() +
  theme_classic()

# plot k = 12, optimized prevalence & content: run = 2

select.pc.12.2 <- tidy(content_prev.model.k12$runout[[2]], matrix = "gamma") %>%
  group_by(topic) %>%
  summarise(gamma = sum(gamma, na.rm = TRUE), .groups = "drop") %>%
  mutate(proportion = (gamma / n_documents) * 100)

select.pc.12.2$topic <- factor(select.pc.12.2$topic, levels = select.pc.12.2[order(select.pc.12.2$proportion, decreasing = FALSE), ]$topic)

m3 <- select.pc.12.2 %>% ggplot(aes(x = topic, y = proportion, fill = proportion)) +
  geom_col(alpha = 0.8, show.legend = FALSE) +
  labs(title = "Topic Prevalence: K = 12, Model 2", subtitle = "Prevalence & Content: selectModel()", y = "Proportion (%)", x = "Topic") +
  coord_flip() +
  theme_classic()

# plot k = 12, prevalence & content single model

stm.pc.k12 <- tidy(stm.pc.12, matrix = "gamma") %>%
  group_by(topic) %>%
  summarise(gamma = sum(gamma, na.rm = TRUE), .groups = "drop") %>%
  mutate(proportion = (gamma / n_documents) * 100)

stm.pc.k12$topic <- factor(stm.pc.k12$topic, levels = stm.pc.k12[order(stm.pc.k12$proportion, decreasing = FALSE), ]$topic)

m4 <- stm.pc.k12 %>% ggplot(aes(x = topic, y = proportion, fill = proportion)) +
  geom_col(alpha = 0.8, show.legend = FALSE) +
  labs(title = "Topic Prevalence: K = 12", subtitle = "Prevalence & Content: stm()", y = "Proportion (%)", x = "Topic") +
  coord_flip() +
  theme_classic()

# plot k = 12, prevalence single model

stm.p.k12 <- tidy(stm.p.12, matrix = "gamma") %>%
  group_by(topic) %>%
  summarise(gamma = sum(gamma, na.rm = TRUE), .groups = "drop") %>%
  mutate(proportion = (gamma / n_documents) * 100)

stm.p.k12$topic <- factor(stm.p.k12$topic, levels = stm.p.k12[order(stm.p.k12$proportion, decreasing = FALSE), ]$topic)

m5 <- stm.p.k12 %>% ggplot(aes(x = topic, y = proportion, fill = proportion)) +
  geom_col(alpha = 0.8, show.legend = FALSE) +
  labs(title = "Topic Prevalence: K = 12", subtitle = "Prevalence: stm()", y = "Proportion (%)", x = "Topic") +
  coord_flip() +
  theme_classic()

m1 | m2 | m3 | m4 | m5
```

Four different types of word weightings are printed with label topics.

Highest Prob: are the words within each topic with the highest probability (inferred directly from topic-word distribution parameter \betaβ).

FREX: are the words that are both frequent and exclusive, identifying words that distinguish topics. This is calculated by taking the harmonic mean of rank by probability within the topic (frequency) and rank by distribution of topic given word p(z|w=v)p(z∣w=v) (exclusivity). In estimating exclusivity we use a James-Stein type shrinkage estimator of the distribution p(z|w=v)p(z∣w=v). More information can be found in the documentation for the internal function calcfrex and js.estimate.

Score and Lift are measures provided in two other popular text mining packages. For more information on type Score, see the R package lda or the internal function calcscore. For more information on type Lift, see the R package maptpx or or the internal function calclift.

*Caution*

stm models using just prevalence formula will display top probability words
stm models using prevalence and content will display top lift words

```{r}
# create and save dataframes for top 10 words per topic and model

l12.a <- labelTopics(stm.model.12, c(1:12), n = 10) # printing highest prob

# l12.b<-labelTopics(content_prev.model.k12$runout[[1]], c(1:12), n=10) # printing lift

# l12.c<-labelTopics(stm.pc.12, c(1:12), n=10) # printing lift

l12.d <- labelTopics(stm.p.12, c(1:12), n = 10) # printing highest prob

# explore marginal top words

sageLabels(stm.model.12)
sageLabels(content_prev.model.k12$runout[[1]])
sageLabels(stm.pc.12)
sageLabels(stm.p.12)

# create tables for top word categories == stm prevalence model

lab12.prob.stm <- l12.d[1] %>%
  as.data.frame() %>% # will collect top 10 lift terms for each topic
  rownames_to_column(var = "topic") %>%
  unite(collapse, !1, remove = FALSE, sep = ", ") %>%
  rename(top_words = collapse) %>%
  select(topic, top_words) %>%
  kable(caption = 'Top Topic Words - "Probability": STM Prevalence Model')

lab12.frex.stm <- l12.d[2] %>%
  as.data.frame() %>% # will collect top 10 lift terms for each topic
  rownames_to_column(var = "topic") %>%
  unite(collapse, !1, remove = FALSE, sep = ", ") %>%
  rename(top_words = collapse) %>%
  select(topic, top_words) %>%
  kable(caption = 'Top Topic Words - "FREX": STM Prevalence Model')

lab12.lift.stm <- l12.d[3] %>%
  as.data.frame() %>% # will collect top 10 lift terms for each topic
  rownames_to_column(var = "topic") %>%
  unite(collapse, !1, remove = FALSE, sep = ", ") %>%
  rename(top_words = collapse) %>%
  select(topic, top_words) %>%
  kable(caption = 'Top Topic Words - "Lift": STM Prevalence Model')

lab12.score.stm <- l12.d[4] %>%
  as.data.frame() %>% # will collect top 10 lift terms for each topic
  rownames_to_column(var = "topic") %>%
  unite(collapse, !1, remove = FALSE, sep = ", ") %>%
  rename(top_words = collapse) %>%
  select(topic, top_words) %>%
  kable(caption = 'Top Topic Words - "Score": STM Prevalence Model')


# compare tables

lab12.prob.stm
lab12.frex.stm
lab12.lift.stm
lab12.score.stm


# another way to plot - plotSTM() cant assign label type to formulas with content

plot(stm.model.12, "labels", topics = c(1:12), width = 1200, labeltype = "prob", n = 10, main = 'Top Topic Words - "Probability": STM Optimized Prevalence Model')

plot(stm.p.12, "labels", labeltype = "prob", width = 1200, topics = c(1:12), n = 10, main = 'Top Topic Words - "Probability": STM Prevalence Model')

# plot distribution of topic proportions -- the two prevalence models produce equivalent results

plot(stm.model.12, "hist", c(1:12), main = "Frequency Distribution of Topics: STM Prevalence Model")

plot(stm.p.12, "hist", c(1:12), main = "Frequency Distribution of Topics: STM Prevalence Model")
```
Use make.dt to create a data table for the model object that we can run queries against 

Combines the document-topic loadings (theta) with metadata to create a data.table object for easy querying.

```{r}
# create document table with and meta variables for stm_18

table.meta <- meta %>%
  select(doc_id, institution, gender, age, race)


t.12 <- make.dt(stm.p.12, meta = table.meta) %>%
  relocate(c(doc_id, institution, gender, age, race), .after = docnum)


# find 5 most associated documents for topic 1

t.12[docnum[order(Topic3, decreasing = TRUE)][1:10]]
```



Document topic proportions and essays - basic stm model

refs:

https://juliasilge.com/blog/sherlock-holmes-stm/
https://github.com/fracab/STMIndeed/blob/master/Indeed%20RJupyterNB2b.ipynb

```{r figure.height=20}
tidy_beta <- tidy(stm.p.12) # prob that each word is generated from each topic


tidy_gamma <- tidy(stm.p.12, matrix = "gamma") # prob that each doc is generated from each topic

tidy_gamma %>%
  filter(document == 1)

# associate docs, topic proportions, metadata

topic_prop12 <- make.dt(stm.p.12, meta)

# display data associations

head(topic_prop12)
```

Plot topic proportions by document

```{r}
# plot gammas

theta_plots <- tidy_gamma[tidy_gamma$document %in% c(1:9), ] # subset data

theta_plots %>% ggplot(aes(y = gamma, x = as.factor(topic), fill = as.factor(topic))) +
  geom_bar(stat = "identity", alpha = 0.8, show.legend = FALSE) +
  facet_wrap(~document, ncol = 3) +
  coord_flip() +
  labs(title = "Topic Proportions By Document (n=8210)", y = expression(theta), x = "Topic")
```

Perspective plot -- compares word probabilities across 2 topics

```{r}
# topic comparisons

plot(stm.p.12, "perspectives", topics = c(8, 12), n = 25, text.cex = 1)

plot(stm.p.12, "perspectives", topics = c(11, 3), n = 25, text.cex = 1)
```

Evaluate covariate main effects on topics -- 12 topics for this purpose. 


*Caution*

This process leverages the meta file to predict prevalence. A model specified for prevalence will produce somewhat different results from one specified for prevalence and content

```{r}
# covariate statistics

gender.pred <- estimateEffect(formula = 1:12 ~ gender, stmobj = stm.p.12, metadata = meta, uncertainty = "Global")

race.pred <- estimateEffect(formula = 1:12 ~ race, stmobj = stm.p.12, metadata = meta, uncertainty = "Global")

first.gen.pred <- estimateEffect(formula = 1:12 ~ first_gen, stmobj = stm.p.12, metadata = meta, uncertainty = "Global")

age.pred <- estimateEffect(formula = 1:12 ~ s(age), stmobj = stm.p.12, metadata = meta, uncertainty = "Global")


# tidy format - filter for significant effects

tidy(gender.pred) %>%
  filter(term != "(Intercept)" & p.value < 0.05)

tidy(race.pred) %>%
  filter(term != "(Intercept)" & p.value < 0.05)

tidy(first.gen.pred) %>%
  filter(term != "(Intercept)" & p.value < 0.05)

tidy(age.pred) %>%
  filter(term != "(Intercept)" & p.value < 0.05)

# summary format -- hash: topics with signf at 0.05

gp <- summary(gender.pred) # 1,2,3,5,7,8,9,11,12
rp <- summary(race.pred) # 2, 4,7,9
fgp <- summary(first.gen.pred) # 7,8,9,12
ag <- summary(age.pred) # 1, 3, 4, 5, 7, 8, 9, 10, 12
```
       

Plot effects - Gender: basic stm model

First Plot - Using first difference type estimate, where topic prevalence for a particular topic is contrasted for two groups

Second Plot - Topical content: plot the influence of covariates as a topical content covariate. A topical content variable allows for the vocabulary used to talk about a particular topic to vary. Note that type = perspective gives the highest probability words.

```{r}
# gender_pred and estimated_pred will produce the same plot

tidy(gender.pred)

plot(gender.pred,
  covariate = "gender", topics = c(1:12), cex = .25,
  model = stm.p.12, method = "difference",
  cov.value1 = "F", cov.value2 = "M",
  xlab = "More Male ... More Female",
  main = "Effect of Gender: K=12 Prevalence",
  xlim = c(-.06, .04), labeltype = "custom",
  custom.labels = topic_labels()
)


# gender comparison

plot(stm.p.12, "perspectives", topics = (1:12), n = 12, text.cex = 1, main = "Gender-Based Vocabulary: Test Anxiety")
```
Plot differences in word content by gender 1,2,3,5,7,8,9,11,12

```{r}
# plot k = 12 model, content only

plot(stm.c.12, "perspectives", topics = c(1), n = 25, text.cex = 1, main = "Topic 1 = Areas for Improvement")
plot(stm.c.12, "perspectives", topics = c(2), n = 25, text.cex = 1, main = "Topic 2 = Developing Writing Skills")
plot(stm.c.12, "perspectives", topics = c(3), n = 25, text.cex = 1, main = "Topic 3 = Test Anxiety")
plot(stm.c.12, "perspectives", topics = c(5), n = 25, text.cex = 1, main = "Topic 5 = Improving Math Skills")
plot(stm.c.12, "perspectives", topics = c(7), n = 25, text.cex = 1, main = "Topic 7 = Transferable Strategies - Academic Success")
plot(stm.c.12, "perspectives", topics = c(8), n = 25, text.cex = 1, main = "Topic 8 = Time Management")
plot(stm.c.12, "perspectives", topics = c(9), n = 25, text.cex = 1, main = "Topic 9 = Getting Right Getting it Done")
plot(stm.c.12, "perspectives", topics = c(11), n = 25, text.cex = 1, main = "Topic 11 = Applying and Retaining Subject Matter")
plot(stm.c.12, "perspectives", topics = c(12), n = 25, text.cex = 1, main = "Topic 12 = Managing Distractions")
```

Plot effects - race. Basic stm prevalence model. This section does not include all of the significant effects. See covariate regressions.

```{r}
tidy(race.pred)

# Guard the contrast values against the levels that actually exist. Before the
# S1-7 harmonisation, WGU wrote "Black" while the other institutions wrote
# "Black or African American", so the group occupied two levels and this plot
# contrasted only WGU's half of it. The levels are now merged, which means the
# literal "Black" no longer matches anything -- estimateEffect() would contrast
# against a level that is not there.
race_levels <- levels(as.factor(meta$race))
stopifnot(all(c("Black or African American", "Asian", "Latinx", "White") %in% race_levels))

plot(race.pred,
  covariate = "race", topics = c(1:12), cex = .25,
  model = stm.p.12, method = "difference",
  cov.value1 = "Black or African American", cov.value2 = "White",
  xlab = "More White ... More Black or African American",
  main = "Effect of Race: K=12",
  xlim = c(-.05, .05), labeltype = "custom",
  custom.labels = topic_labels()
)

plot(race.pred,
  covariate = "race", topics = c(1:12), cex = .25,
  model = stm.p.12, method = "difference",
  cov.value1 = "Asian", cov.value2 = "White",
  xlab = "More White ... More Asian",
  main = "Effect of Race: K=12",
  xlim = c(-.05, .05), labeltype = "custom",
  custom.labels = topic_labels()
)

plot(race.pred,
  covariate = "race", topics = c(1:12), cex = .25,
  model = stm.p.12, method = "difference",
  cov.value1 = "Latinx", cov.value2 = "White",
  xlab = "More White ... More Latinx",
  main = "Effect of Race: K=12",
  xlim = c(-.05, .05), labeltype = "custom",
  custom.labels = topic_labels()
)
```


plot effects of first gen - basic stm model

```{r}
tidy(first.gen.pred)

plot(first.gen.pred,
  covariate = "first_gen", topics = c(1:12), Text.cex = .25,
  model = stm.p.12, method = "difference",
  cov.value1 = "FALSE", cov.value2 = "TRUE",
  xlab = "More First Generation ... Less First Generation",
  main = "Effect of First Generation",
  xlim = c(-.04, .02), labeltype = "custom",
  custom.labels = topic_labels()
)
```

Topic prevalence as a function of Age - basic stm prevalence model

Age is a statistically significant covariate for the following topics  1, 3, 4, 5, 7, 8, 9, 10, 12

```{r}
plot_age <- function(effect, covariate, topic_num, model) {
  for (i in topic_num) {
    plot(effect, covariate,
      method = "continuous", topics = i, model = model, printlegend = FALSE, # legend True will print the topic number
      xlab = "Age", main = str_glue("Topic Prevalence as a Function of Age: Topic {i}")
    )
  }
}

plot_age(age.pred, "age", c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12), stm.p.12)
```

Plot age & gender interactions - basic stm prevalence model

```{r}
# build estimate effect formula

interact.signf <- estimateEffect(formula = c(1:12) ~ gender * age, stmobj = stm.p.12, metadata = meta, uncertainty = "Global")

# evaluate statistical significance of interaction

tidy(interact.signf) %>%
  filter(term != "(Intercept)" & p.value < 0.1)

# summary format

gender.age <- summary(interact.signf) # 2,4,6

# plot the significant interactions of age and gender

c2 <- estimateEffect(formula = c(2) ~ gender * age, stmobj = stm.p.12, metadata = meta, uncertainty = "Global")
c4 <- estimateEffect(formula = c(4) ~ gender * age, stmobj = stm.p.12, metadata = meta, uncertainty = "Global")
c6 <- estimateEffect(formula = c(6) ~ gender * age, stmobj = stm.p.12, metadata = meta, uncertainty = "Global")


# topic 2


plot(c2,
  covariate = "age", model = interact.signf, method = "continuous", xlab = "Age",
  moderator = "gender", moderator.value = "M", linecol = "blue", ylim = c(0, .1),
  printlegend = FALSE, main = "Topic 2: Developing Writing Skills (P < 0.10)"
)

plot(c2,
  covariate = "age", model = interact.signf, method = "continuous", xlab = "Age",
  moderator = "gender", moderator.value = "F", linecol = "red", add = TRUE,
  printlegend = FALSE
)

legend(18, .1, c("Male", "Female"), lwd = 2, col = c("blue", "red"))


# topic 4

plot(c4,
  covariate = "age", model = interact.signf, method = "continuous", xlab = "Age",
  moderator = "gender", moderator.value = "M", linecol = "blue", ylim = c(.04, .18),
  printlegend = FALSE, main = "Topic 4. Returning Learners-Degree Completion (P < 0.10)"
)

plot(c4,
  covariate = "age", model = interact.signf, method = "continuous", xlab = "Age",
  moderator = "gender", moderator.value = "F", linecol = "red", add = TRUE,
  printlegend = FALSE
)

legend(18, 0.18, c("Male", "Female"), lwd = 2, col = c("blue", "red"))


# topic 6

plot(c6,
  covariate = "age", model = interact.signf, method = "continuous", xlab = "Age",
  moderator = "gender", moderator.value = "M", linecol = "blue", ylim = c(0, .15),
  printlegend = FALSE, main = "Topic 6: Confirmation and Readiness (P < 0.10)"
)

plot(c6,
  covariate = "age", model = interact.signf, method = "continuous", xlab = "Age",
  moderator = "gender", moderator.value = "F", linecol = "red", add = TRUE,
  printlegend = FALSE
)

legend(18, 0.15, c("Male", "Female"), lwd = 2, col = c("blue", "red"))
```
Create network plot for topics. Assign a cutoff threshold of 0.05

See: https://rdrr.io/cran/stm/src/R/topicCorr.R

```{r}
mod.out.corr <- topicCorr(stm.p.12, method = "simple", cutoff = .05)

plot(mod.out.corr, main = "K=12: Topic Network (P < 0.05)", vlabels = topic_labels(), vertex.label.cex = 0.75, label.color = "darkred", vertex.color = "lightblue")
```
