---
title: "STM  Models"
author: 'Sean Connin'
date: "05/27/22"
output:
  html_document: 
    toc: TRUE
    toc-title: ""
    toc_depth: 3
    toc_float: 
      collapsed: TRUE
      smooth_scroll: FALSE
    number_sections: true
    df_print: paged
    code_folding: hide
    theme: sandstone
    highlight: tango
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Load libraries

```{r}
# The tidyverse core, loaded explicitly rather than through the umbrella
# package. `library(tidyverse)` also pulls in `ragg`, which needs the
# harfbuzz/fribidi system libraries -- a build dependency this analysis never
# uses, and one that makes the project fail to install on a clean machine.
# These are the same namespaces `library(tidyverse)` attaches, minus
# `lubridate` (no date handling anywhere in the pipeline).
library(dplyr)
library(ggplot2)
library(tibble)
library(tidyr)
library(readr)
library(purrr)
library(stringr)
library(forcats)
library(magrittr)
library(stm)
```

Load preprocessed data (.csv format) for additional treatment and partitioning via. stm's textProcessor() function. 

```{r}
# load .csv from local directory

stm_data_final <- read_csv("stm_data_final.csv")
```

The result is a list of four objects: documents, vocab, meta, and docs.removed. The documents object is a list, one per document, of 2 row matrices; the first row indicates the index of a word found in the document, and the second row indicates the (nonzero) counts. If preprocessing causes any documents to be empty, they are removed, as are the corresponding rows of the meta object.

These objects are, in turn, passed to the prepDocuments function, which filters vocabulary, and again removes empty documents and corresponding rows in the metadata (which contains the doc_id, covariates, and text). 

```{r}
set.seed(92200002)


# process data -- stopwords, stemming retained, removes other grammatical elements that were removed in preprocess.rmd

processed <- textProcessor(stm_data_final$text, metadata = stm_data_final, removepunctuation = FALSE, removestopwords = TRUE, stem = TRUE, removenumbers = TRUE, striphtml = TRUE)

# Partition as stm requires, dropping words that occur in <= 1% or >= 99% of
# documents.
#
# The thresholds stay hard-coded at 82 / 8128 DELIBERATELY. They are described in
# prose as 1% and 99%, and stopped meaning that the moment the corpus size
# changed (CODE_REVIEW.md S3-3) -- but deriving them now would alter the
# vocabulary and therefore every fitted model. That is a larger change than the
# correctness fixes in this batch, and it would confound attribution when the
# models are re-fitted. The report below makes the drift visible; converting
# them to derived values is a separate decision.
partition <- prepDocuments(
  processed$documents, processed$vocab, processed$meta,
  lower.thresh = 82, upper.thresh = 8128
)

documents <- partition$documents
vocab <- partition$vocab
meta <- partition$meta

# Report the real dimensions rather than recording them in a comment that goes
# stale. The previous comment claimed "8210 documents, 12440 words"; the corpus
# actually holds 1,254 vocabulary terms, so the word count had been wrong for
# some time (CODE_REVIEW.md S1-5).
n_input <- length(processed$documents)
cat(
  "corpus:", length(documents), "documents,", length(vocab), "vocabulary terms\n",
  "thresholds 82/8128 represent",
  sprintf("%.2f%%", 100 * 82 / n_input), "and",
  sprintf("%.2f%%", 100 * 8128 / n_input),
  "of the", n_input, "documents entering prepDocuments()\n"
)

# Save prepDocuments results. This write was commented out, but three notebooks
# load the file it produces, so the pipeline could not run from a clean
# checkout without it. `meta` carries essay text and demographics and is
# IRB-protected; .gitignore excludes *.Rdata so it stays local.

save(documents, vocab, meta, file = "processed_corpus_final.Rdata")
```

## Scope: K = 12 only

The original sweep fitted five families across K = 6/12/18/24/32 — 21 model calls,
two of which run 10 internal candidates each. **This file now fits K = 12 only.**

K was not selected by exclusivity and coherence. It was settled by professional
review of the clustering results across the candidate models, and that review is
complete: K = 12 is final. Re-fitting K = 6/18/24/32 would regenerate inputs to a
decision already made, at the majority of the compute cost (the large-K fits
dominate the sweep).

The corrections that prompted this re-fit do not bear on the choice of K. The
gender fix moves 134 of 8,210 documents (1.6%), the race fix merges level labels
without changing which essays are present, and the proportion and corpus-size
fixes are arithmetic applied downstream of the model. None plausibly changes what
a human reviewing exemplar essays judged to be the most coherent topic count.

**The K-sweep code is retained, commented out, in each block below.** If the
corpus ever changes enough to warrant revisiting K, restore those lines rather
than reconstructing them. See CODE_REVIEW.md.

Five distinct K = 12 models are still fitted, one per family — they differ in
specification, not in K, and `stm_analyses_final.Rmd` compares all five.

Build the optimized prevalence model using manyTopics(). This function accepts
only a prevalence formula.

```{r}
# manyTopics() loops over K internally, so a single K is valid: it runs once and
# returns the fitted model as out[[1]].

system.time({
  ## elapsed time for the full K = 6..32 sweep was 2286.47s; K = 12 alone is a
  ## fraction of that.

  select.models <- manyTopics(documents, vocab,
    data = meta, K = 12,
    prevalence = ~ gender + race + first_gen + s(age) + gender * s(age),
    runs = 10, init.type = "Spectral", seed = 811235359
  )
})

stm.model.12 <- select.models$out[[1]]

# Retained for a future K sweep:
#
# select.models <- manyTopics(documents, vocab,
#   data = meta, K = c(6, 12, 18, 24, 32),
#   prevalence = ~ gender + race + first_gen + s(age) + gender * s(age),
#   runs = 10, init.type = "Spectral", seed = 811235359
# )
# stm.model.6  <- select.models$out[[1]]
# stm.model.12 <- select.models$out[[2]]
# stm.model.18 <- select.models$out[[3]]
# stm.model.24 <- select.models$out[[4]]
# stm.model.32 <- select.models$out[[5]]

save(stm.model.12, file = "optimized.prevalence.model.k12.Rda")
```
Due to the fact that manyTopics only enables a prevalence formula, use the stm() method to model both prevalence and content in a single declaration. The method is applied here to models with K = 6 to 32. Similar to manyTopics, an optimized model for each K based on exclusivity and coherence.

In this latter respect, the use of manyTopics is redundant and is included here for comparison. 

```{r}
# fit stm models with content + prevalence formulas

content_prev.model.k12 <- selectModel(documents, vocab,
  data = meta, K = 12,
  prevalence = ~ gender + race + first_gen + s(age) + gender * s(age),
  content = ~gender, max.em.its = 75, runs = 10, seed = 845815922
)

# Retained for a future K sweep (seeds as originally assigned):
#
# content_prev.model.k6 <- selectModel(documents, vocab,
#   data = meta, K = 6, ..., seed = 845815921)
# content_prev.model.k18 <- selectModel(documents, vocab,
#   data = meta, K = 18, ..., seed = 845815923)
# content_prev.model.k24 <- selectModel(documents, vocab,
#   data = meta, K = 24, ..., seed = 84581524)
# content_prev.model.k32 <- selectModel(documents, vocab,
#   data = meta, K = 32, ..., seed = 841158925)

save(content_prev.model.k12, file = "optimized.prevalence.content.model.k12.Rda")

# print quick diagnostics

# plotModels(content_prev.model.k12)
```

Build prevalence & content formula models without optimization: basic stm() method

```{r}
# fit stm models for prevalence & content without optimization

stm.pc.12 <- stm(documents, vocab,
  data = meta, K = 12,
  prevalence = ~ gender + race + first_gen + s(age) + gender * s(age),
  content = ~gender, max.em.its = 75, seed = 784654
)

# Retained for a future K sweep (seeds as originally assigned):
#
# stm.pc.6  <- stm(documents, vocab, data = meta, K = 6,  ..., seed = 784653)
# stm.pc.18 <- stm(documents, vocab, data = meta, K = 18, ..., seed = 784655)
# stm.pc.24 <- stm(documents, vocab, data = meta, K = 24, ..., seed = 784656)
# stm.pc.32 <- stm(documents, vocab, data = meta, K = 32, ..., seed = 784657)

save(stm.pc.12, file = "stm.prevalence.content.model.k12.Rda")
```
Build prevalence formula model without optimization: basic stm() method

**These two families previously passed no `seed=`** — the only families in this
file that did not (`CODE_REVIEW.md` S3-1). Spectral initialization and EM are not
deterministic without one, so the published `stm.p.12` could not be reproduced,
and `stm.p.12` is the model that drives every `estimateEffect()` result and the
topic-correlation network in `stm_analyses_final.Rmd`.

Seeds are added here. Because the previous run was unseeded, its exact fit is
unrecoverable regardless — so adding them now costs nothing and makes this run,
the one carrying every correction, reproducible.

```{r}
stm.p.12 <- stm(documents, vocab,
  data = meta, K = 12,
  prevalence = ~ gender + race + first_gen + s(age) + gender * s(age),
  init.type = "Spectral", max.em.its = 75, seed = 784658
)

# Retained for a future K sweep:
#
# stm.p.6  <- stm(documents, vocab, data = meta, K = 6,  ..., seed = 784659)
# stm.p.18 <- stm(documents, vocab, data = meta, K = 18, ..., seed = 784660)
# stm.p.24 <- stm(documents, vocab, data = meta, K = 24, ..., seed = 784661)
# stm.p.32 <- stm(documents, vocab, data = meta, K = 32, ..., seed = 784662)

save(stm.p.12, file = "stm.prevalence.model.k12.Rda")
```

Build content formula without optimization: basic stm() method.

```{r}
stm.c.12 <- stm(documents, vocab,
  data = meta, K = 12,
  content = ~gender, init.type = "Spectral", max.em.its = 75, seed = 784663
)

# Retained for a future K sweep:
#
# stm.c.6  <- stm(documents, vocab, data = meta, K = 6,  ..., seed = 784664)
# stm.c.18 <- stm(documents, vocab, data = meta, K = 18, ..., seed = 784665)
# stm.c.24 <- stm(documents, vocab, data = meta, K = 24, ..., seed = 784666)
# stm.c.32 <- stm(documents, vocab, data = meta, K = 32, ..., seed = 784667)

save(stm.c.12, file = "stm.content.model.k12.Rda")
```

