---
title: "STM  Models"
author: 'Sean Connin'
date: "05/27/22"
output:
  html_document: 
    toc: TRUE
    toc-title: ""
    toc_depth: 3
    toc_float: 
      collapsed: TRUE
      smooth_scroll: FALSE
    number_sections: true
    df_print: paged
    code_folding: hide
    theme: sandstone
    highlight: tango
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Load libraries

```{r}
library(tidyverse)
library(magrittr)
library(stm)
```

Load preprocessed data (.csv format) for additional treatment and partitioning via. stm's textProcessor() function. 

```{r}
# load .csv from local directory

stm_data_final <- read_csv("stm_data_final.csv")
```

The result is a list of four objects: documents, vocab, meta, and docs.removed. The documents object is a list, one per document, of 2 row matrices; the first row indicates the index of a word found in the document, and the second row indicates the (nonzero) counts. If preprocessing causes any documents to be empty, they are removed, as are the corresponding rows of the meta object.

These objects are, in turn, passed to the prepDocuments function, which filters vocabulary, and again removes empty documents and corresponding rows in the metadata (which contains the doc_id, covariates, and text). 

```{r}
set.seed(92200002)


# process data -- stopwords, stemming retained, removes other grammatical elements that were removed in preprocess.rmd

processed <- textProcessor(stm_data_final$text, metadata = stm_data_final, removepunctuation = FALSE, removestopwords = TRUE, stem = TRUE, removenumbers = TRUE, striphtml = TRUE)

# Partition as stm requires, dropping words that occur in <= 1% or >= 99% of
# documents.
#
# The thresholds stay hard-coded at 82 / 8128 DELIBERATELY. They are described in
# prose as 1% and 99%, and stopped meaning that the moment the corpus size
# changed (CODE_REVIEW.md S3-3) -- but deriving them now would alter the
# vocabulary and therefore every fitted model. That is a larger change than the
# correctness fixes in this batch, and it would confound attribution when the
# models are re-fitted. The report below makes the drift visible; converting
# them to derived values is a separate decision.
partition <- prepDocuments(
  processed$documents, processed$vocab, processed$meta,
  lower.thresh = 82, upper.thresh = 8128
)

documents <- partition$documents
vocab <- partition$vocab
meta <- partition$meta

# Report the real dimensions rather than recording them in a comment that goes
# stale. The previous comment claimed "8210 documents, 12440 words"; the corpus
# actually holds 1,254 vocabulary terms, so the word count had been wrong for
# some time (CODE_REVIEW.md S1-5).
n_input <- length(processed$documents)
cat(
  "corpus:", length(documents), "documents,", length(vocab), "vocabulary terms\n",
  "thresholds 82/8128 represent",
  sprintf("%.2f%%", 100 * 82 / n_input), "and",
  sprintf("%.2f%%", 100 * 8128 / n_input),
  "of the", n_input, "documents entering prepDocuments()\n"
)

# save prepDocuments results to local directory

# save(documents, vocab, meta, file ="processed_corpus_final.Rdata")  # rda - saves multiple files
```

Build set of models (K = 6 to 32) optimized via. exclusivity & coherence measures using manyTopics(). Note that this function only accepts prevalence models. 

```{r}
# Perform model selection across separate STM’s that each assume different numbers of topics

system.time({
  ## elapsed time 2286.47

  # build models using manyTopics

  select.models <- manyTopics(documents, vocab,
    data = meta, K = c(6, 12, 18, 24, 32),
    prevalence = ~ gender + race + first_gen + s(age) + gender * s(age),
    runs = 10, init.type = "Spectral", seed = 811235359
  )
})

# separate models

stm.model.6 <- select.models$out[[1]]
stm.model.12 <- select.models$out[[2]]
stm.model.18 <- select.models$out[[3]]
stm.model.24 <- select.models$out[[4]]
stm.model.32 <- select.models$out[[5]]

# save optimized models to local directory

save(stm.model.6,
  stm.model.12,
  stm.model.18,
  stm.model.24,
  stm.model.32,
  file = "optimized.prevalence.models.6_32.Rda"
)
```
Due to the fact that manyTopics only enables a prevalence formula, use the stm() method to model both prevalence and content in a single declaration. The method is applied here to models with K = 6 to 32. Similar to manyTopics, an optimized model for each K based on exclusivity and coherence.

In this latter respect, the use of manyTopics is redundant and is included here for comparison. 

```{r}
# fit stm models with content + prevalence formulas

content_prev.model.k6 <- selectModel(documents, vocab,
  data = meta, K = 6,
  prevalence = ~ gender + race + first_gen + s(age) + gender * s(age),
  content = ~gender, max.em.its = 75, runs = 10, seed = 845815921
)

content_prev.model.k12 <- selectModel(documents, vocab,
  data = meta, K = 12,
  prevalence = ~ gender + race + first_gen + s(age) + gender * s(age),
  content = ~gender, max.em.its = 75, runs = 10, seed = 845815922
)

content_prev.model.k18 <- selectModel(documents, vocab,
  data = meta, K = 18,
  prevalence = ~ gender + race + first_gen + s(age) + gender * s(age),
  content = ~gender, max.em.its = 75, runs = 10, seed = 845815923
)

content_prev.model.k24 <- selectModel(documents, vocab,
  data = meta, K = 24,
  prevalence = ~ gender + race + first_gen + s(age) + gender * s(age),
  content = ~gender, max.em.its = 75, runs = 10, seed = 84581524
)

content_prev.model.k32 <- selectModel(documents, vocab,
  data = meta, K = 32,
  prevalence = ~ gender + race + first_gen + s(age) + gender * s(age),
  content = ~gender, max.em.its = 75, runs = 10, seed = 841158925
)

# save content-prevalence (selected) models to local directory

save(content_prev.model.k6,
  content_prev.model.k12,
  content_prev.model.k18,
  content_prev.model.k24,
  content_prev.model.k32,
  file = "optimized.prevalence.content.models.6_32.Rda"
)

# print quick diagnostics

# plotModels(content_prev.model.k6)
# plotModels(content_prev.model.k12)
# plotModels(content_prev.model.k18)
# plotModels(content_prev.model.k24)
# plotModels(content_prev.model.k32)
```

Build prevalence & content formula models without optimization: basic stm() method

```{r}
# fit stm models for prevalence & content without optimization

stm.pc.6 <- stm(documents, vocab,
  data = meta, K = 6,
  prevalence = ~ gender + race + first_gen + s(age) + gender * s(age),
  content = ~gender, max.em.its = 75, seed = 784653
)

stm.pc.12 <- stm(documents, vocab,
  data = meta, K = 12,
  prevalence = ~ gender + race + first_gen + s(age) + gender * s(age),
  content = ~gender, max.em.its = 75, seed = 784654
)

stm.pc.18 <- stm(documents, vocab,
  data = meta, K = 18,
  prevalence = ~ gender + race + first_gen + s(age) + gender * s(age),
  content = ~gender, max.em.its = 75, seed = 784655
)

stm.pc.24 <- stm(documents, vocab,
  data = meta, K = 24,
  prevalence = ~ gender + race + first_gen + s(age) + gender * s(age),
  content = ~gender, max.em.its = 75, seed = 784656
)

stm.pc.32 <- stm(documents, vocab,
  data = meta, K = 32,
  prevalence = ~ gender + race + first_gen + s(age) + gender * s(age),
  content = ~gender, max.em.its = 75, seed = 784657
)

# save stm content-prevalence models to local directory

save(stm.pc.6,
  stm.pc.12,
  stm.pc.18,
  stm.pc.24,
  stm.pc.32,
  file = "stm.prevalence.content.models.6_32.Rda"
)
```
Build prevalence formula model without optimization: basic stm() method

```{r}
stm.p.6 <- stm(documents, vocab,
  data = meta, K = 6,
  prevalence = ~ gender + race + first_gen + s(age) + gender * s(age), init.type = "Spectral", max.em.its = 75
)

stm.p.12 <- stm(documents, vocab,
  data = meta, K = 12,
  prevalence = ~ gender + race + first_gen + s(age) + gender * s(age), init.type = "Spectral", max.em.its = 75
)

stm.p.18 <- stm(documents, vocab,
  data = meta, K = 18,
  prevalence = ~ gender + race + first_gen + s(age) + gender * s(age), init.type = "Spectral", max.em.its = 75
)

stm.p.24 <- stm(documents, vocab,
  data = meta, K = 24,
  prevalence = ~ gender + race + first_gen + s(age) + gender * s(age), init.type = "Spectral", max.em.its = 75
)

stm.p.32 <- stm(documents, vocab,
  data = meta, K = 32,
  prevalence = ~ gender + race + first_gen + s(age) + gender * s(age), init.type = "Spectral", max.em.its = 75
)


save(stm.p.6, stm.p.12, stm.p.18, stm.p.24, stm.p.32, file = "stm.prevalence.models.6_32.Rda")
```

Build content formula without optimization:basic stm() method. Use same seed.

```{r}
stm.c.6 <- stm(documents, vocab,
  data = meta, K = 6,
  content = ~gender, init.type = "Spectral", max.em.its = 75
)

stm.c.12 <- stm(documents, vocab,
  data = meta, K = 12,
  content = ~gender, init.type = "Spectral", max.em.its = 75
)

stm.c.18 <- stm(documents, vocab,
  data = meta, K = 18,
  content = ~gender, init.type = "Spectral", max.em.its = 75
)

stm.c.24 <- stm(documents, vocab,
  data = meta, K = 24,
  content = ~gender, init.type = "Spectral", max.em.its = 75
)

stm.c.32 <- stm(documents, vocab,
  data = meta, K = 32,
  content = ~gender, init.type = "Spectral", max.em.its = 75
)


save(stm.c.6, stm.c.12, stm.c.18, stm.c.24, stm.c.32, file = "stm.content.models.6_32.Rda")
```

