---
title: "DAACS - STM ANALYSES"
author: "Sean Connin"
date: "05/27/22"
output:
  html_document: 
    toc: TRUE
    toc-title: ""
    toc_depth: 3
    toc_float: 
      collapsed: TRUE
      smooth_scroll: FALSE
    number_sections: true
    df_print: paged
    code_folding: hide
    theme: sandstone
    highlight: tango
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

load libraries

```{r}
# The tidyverse core, loaded explicitly rather than through the umbrella
# package. `library(tidyverse)` also pulls in `ragg`, which needs the
# harfbuzz/fribidi system libraries -- a build dependency this analysis never
# uses, and one that makes the project fail to install on a clean machine.
# These are the same namespaces `library(tidyverse)` attaches, minus
# `lubridate` (no date handling anywhere in the pipeline).
library(dplyr)
library(ggplot2)
library(tibble)
library(tidyr)
library(readr)
library(purrr)
library(stringr)
library(forcats)
library(magrittr)
library(stm)
library(igraph) # network graph
library(huge) # network graph
library(tidytext)
library(patchwork)

# Shared helpers. Every computation this notebook repeats across model families
# is defined once in R/ and tested in tests/testthat/.
source("R/topic_labels.R") # TOPIC_LABELS_K12, topic_labels()
source("R/topic_prevalence.R") # topic_proportions(), plot_topic_proportions()
source("R/topic_word_tables.R") # topic_word_table(), topic_word_tables()
source("R/covariate_effects.R") # estimate_effects(), significant_effects(), plots
```

Two libraries were dropped from this block. `httr` was declared here and in two
other notebooks but never called. `kableExtra` was declared but never used
either: the four tables below call `kable()`, which comes from **knitr**, not
from `kableExtra` -- no `kable_styling()`, `column_spec()` or other extension
function appears anywhere in this file.

That distinction matters practically, not just tidily. `kableExtra` depends on
`svglite` -> `systemfonts`/`textshaping`, which need the harfbuzz and fribidi
system headers; without them `install.packages("kableExtra")` fails and this
notebook cannot run at all. Dropping an unused dependency removed that blocker.
See `CODE_REVIEW.md` S4.

Load corpus, kresult, and models -- from preprocess_data_final and stm topic models

Models loaded in this file. Each file is written by stm_models_final.Rmd; the object names below are
what `load()` restores into the global environment, so they are the names to reference downstream.

| File | Object | Fitted by | Formula |
|---|---|---|---|
| optimized.prevalence.model.k12.Rda | `stm.model.12` | `manyTopics()` | prevalence |
| optimized.prevalence.content.model.k12.Rda | `content_prev.model.k12` | `selectModel()` | prevalence + content |
| stm.prevalence.content.model.k12.Rda | `stm.pc.12` | `stm()` | prevalence + content |
| stm.prevalence.model.k12.Rda | `stm.p.12` | `stm()` | prevalence |
| stm.content.model.k12.Rda | `stm.c.12` | `stm()` | content |

Note: "optimized" refers to automatic selection based on high-likelihood values. The `selectModel()`
families return a list, so those objects are indexed as `$runout[[n]]` rather than used directly.

**K = 12 only.** These five models differ in specification, not in topic count. K was settled by
professional review of the clustering results across candidate models rather than by exclusivity and
coherence, and that review is complete — so `stm_models_final.rmd` no longer re-fits K = 6/18/24/32.
Every analysis in this file already referenced K = 12 exclusively; the one exception was the
exclusivity-vs-coherence comparison below, which is now inert. See `CODE_REVIEW.md`.

```{r}
# load processed corpus - documents, vocab, meta

processed <- load("processed_corpus_final.Rdata")

# load optimized prevalence models

prev.models <- load("optimized.prevalence.model.k12.Rda")

# load optimized prevalence & content models

prev.content.models <- load("optimized.prevalence.content.model.k12.Rda")

# load basic stm prevalence & content models

prev.content.stm <- load("stm.prevalence.content.model.k12.Rda")

# load basic stm prevalence model

prev.stm <- load("stm.prevalence.model.k12.Rda")

# load basic stm content model

content.stm <- load("stm.content.model.k12.Rda")
```

Load raw essays and bind to filtered identifiers (doc_id, institution) - original text less any essays filtered out during preprocessing. 

```{r}
# subset doc_id and text from prepDocuments output

filtered <- meta %>%
  select(doc_id, institution, text)

# load raw data

preclean <- read_csv("preclean_text.csv", show_col_types = FALSE)

# Join on doc_id AND institution. doc_id is unique only WITHIN an institution;
# the three sources reuse the same numeric ids, so joining on doc_id alone
# matches essays across institutions (CODE_REVIEW.md S1-10).
#
# As written -- `left_join(filter_id, preclean, by = "doc_id")` -- this produced
# 10,224 rows from an 8,210-document corpus, and all 2,014 extra rows paired a
# student with another institution's essay text. It was also row-misaligned with
# the model, which matters because findThoughts() indexes texts positionally.
#
# The object was never actually read in this file, so no published result is
# affected -- but the comment above advertises it "for use in topic exemplar
# review", which is exactly the use that would have been wrong.
# essay_examples_final.Rmd already joins on both keys.

original <- inner_join(
  filtered %>% select(doc_id, institution),
  preclean,
  by = c("doc_id", "institution")
)

stopifnot(nrow(original) == nrow(meta))
```

## Exclusivity vs. coherence across K — not run

This was the one section of this file that required the full K sweep. It is retained as a record of
the diagnostic that was computed, but **it is not part of how K was chosen**: the selection was made
by professional review of the clustering results across candidate models, not by these two measures.
Since `stm_models_final.rmd` now fits K = 12 only, `stm.model.6/18/24/32` do not exist and this code
would error.

To restore it, un-comment the K sweep in `stm_models_final.rmd` and this chunk together — they are a
pair. The chunk is marked `eval = FALSE` so the notebook knits without it.

These plots cannot be graphed when a content formula is included.

```{r eval = FALSE}
# build dataframes with exclusivity and coherence measures for each optimized model

CE6 <- as.data.frame(cbind(c(1:6), exclusivity(stm.model.6), semanticCoherence(model = stm.model.6, documents), "Mod6"))
CE12 <- as.data.frame(cbind(c(1:12), exclusivity(stm.model.12), semanticCoherence(model = stm.model.12, documents), "Mod12"))
CE18 <- as.data.frame(cbind(c(1:18), exclusivity(stm.model.18), semanticCoherence(model = stm.model.18, documents), "Mod18"))
CE24 <- as.data.frame(cbind(c(1:24), exclusivity(stm.model.24), semanticCoherence(model = stm.model.24, documents), "Mod24"))
CE32 <- as.data.frame(cbind(c(1:32), exclusivity(stm.model.32), semanticCoherence(model = stm.model.32, documents), "Mod32"))

# combine diagnostics for each model

CE6_32 <- rbind(CE6, CE12, CE18, CE24, CE32)

# reset column names

colnames(CE6_32) <- c("K", "Exclusivity", "SemanticCoherence", "Model")

# reset feature types

CE6_32$Exclusivity <- as.numeric(as.character(CE6_32$Exclusivity))
CE6_32$SemanticCoherence <- as.numeric(as.character(CE6_32$SemanticCoherence))

CE6_32$Model <- factor(CE6_32$Model, levels = c("Mod6", "Mod12", "Mod18", "Mod24", "Mod32"))

# save(CE6_32, file="exclusivity_coherence6-28.Rdata")

# build exclusivity & coherence plot for models

plot <- ggplot(CE6_32, aes(SemanticCoherence, Exclusivity, color = Model)) +
  geom_point(size = 2, alpha = 0.7) +
  geom_text(aes(label = K), nudge_x = .09, nudge_y = .09, size = 2.5) +
  labs(
    x = "Semantic coherence",
    y = "Exclusivity",
    title = "Model Diagnostics: Exclusivity and Semantic Coherence",
    subtitle = "Prevalence Formula: manyTopics()"
  ) +
  theme_classic()
```






Plot topic quality  and prevalence for K = 12, prevalence model and basic STM. Highest probability words.

```{r}
# Plot topic quality by model (coherence & exclusivity)

topicQuality(stm.model.12, documents)
```

Compare topic prevalence across optimized and non-optimized models for K=12

```{r}
# plot topic prevalence across documents

plot(stm.model.12, main = "Topic Prevalence - K12 (manyTopics)") # highest probability words

# plot topic prevalence basic stm model

plot(stm.p.12, main = "Topic Prevalence - K12 (STM)")
```
It is possible to create a topic prevalence plot using models built on prevalence & content formula. This was not possible with the topicQuality() function. In this context, we can compare differencesin models (with same K) that pass the optimization process.

Note that the results will also be different from the optimized model built on prevalence formula alone, owing to different initializations and model selection. 

```{r}
# Each document's topic proportions sum to 1, so summing gamma across documents
# and dividing by the document count gives the mean proportion per topic.
#
# Five near-identical blocks stood here, one per model family, differing only in
# which model they read and what the subtitle said. They are now one call each to
# topic_proportions() + plot_topic_proportions() (R/topic_prevalence.R), which is
# also where the two corrections live rather than being repeated five times
# (CODE_REVIEW.md S1-4, S1-5):
#
#   - The divisor was hard-coded as 8120. The corpus holds 8210 documents --
#     the same digits transposed. It is now derived, and asserted against the
#     value recorded when the corpus was built.
#   - The sum was written `sum(., is.na(.), 0)`. sum() is variadic, so that
#     added the COUNT OF NAs to the total rather than removing them.
n_documents <- length(documents)
stopifnot(n_documents == 8210)

prevalence_specifications <- list(
  list(
    model = stm.model.12,
    title = "Topic Prevalence within Corpus: K = 12",
    subtitle = "Topic Prevalence: manyTopics()"
  ),
  list(
    model = content_prev.model.k12$runout[[1]],
    title = "Topic Prevalence: K = 12, Model 1",
    subtitle = "Prevalence & Content: selectModel()"
  ),
  list(
    model = content_prev.model.k12$runout[[2]],
    title = "Topic Prevalence: K = 12, Model 2",
    subtitle = "Prevalence & Content: selectModel()"
  ),
  list(
    model = stm.pc.12,
    title = "Topic Prevalence: K = 12",
    subtitle = "Prevalence & Content: stm()"
  ),
  list(
    model = stm.p.12,
    title = "Topic Prevalence: K = 12",
    subtitle = "Prevalence: stm()"
  )
)

prevalence_plots <- lapply(prevalence_specifications, function(spec) {
  plot_topic_proportions(
    topic_proportions(spec$model, n_documents),
    title = spec$title,
    subtitle = spec$subtitle
  )
})

patchwork::wrap_plots(prevalence_plots, nrow = 1)
```

Four different types of word weightings are printed with label topics.

Highest Prob: are the words within each topic with the highest probability (inferred directly from topic-word distribution parameter \betaβ).

FREX: are the words that are both frequent and exclusive, identifying words that distinguish topics. This is calculated by taking the harmonic mean of rank by probability within the topic (frequency) and rank by distribution of topic given word p(z|w=v)p(z∣w=v) (exclusivity). In estimating exclusivity we use a James-Stein type shrinkage estimator of the distribution p(z|w=v)p(z∣w=v). More information can be found in the documentation for the internal function calcfrex and js.estimate.

Score and Lift are measures provided in two other popular text mining packages. For more information on type Score, see the R package lda or the internal function calcscore. For more information on type Lift, see the R package maptpx or or the internal function calclift.

*Caution*

stm models using just prevalence formula will display top probability words
stm models using prevalence and content will display top lift words

```{r}
# create and save dataframes for top 10 words per topic and model

l12.a <- labelTopics(stm.model.12, c(1:12), n = 10) # printing highest prob

# l12.b<-labelTopics(content_prev.model.k12$runout[[1]], c(1:12), n=10) # printing lift

# l12.c<-labelTopics(stm.pc.12, c(1:12), n=10) # printing lift

l12.d <- labelTopics(stm.p.12, c(1:12), n = 10) # printing highest prob

# explore marginal top words

sageLabels(stm.model.12)
sageLabels(content_prev.model.k12$runout[[1]])
sageLabels(stm.pc.12)
sageLabels(stm.p.12)

# create tables for top word categories == stm prevalence model
#
# Four near-identical blocks stood here, differing only in which element of
# labelTopics() they read and what the caption said. topic_word_tables()
# (R/topic_word_tables.R) returns all four, named.
lab12.stm <- topic_word_tables(l12.d)


# compare tables
#
# Read all four before judging what a topic is about. prob and frex favour
# frequent terms; lift and score surface the low-frequency, distinctive terms
# that identify the subject. Reading only the first two led to topic 5 being
# called mathematics-free when lift and score both lead with `mathemat`.

lab12.stm$prob
lab12.stm$frex
lab12.stm$lift
lab12.stm$score


# another way to plot - plotSTM() cant assign label type to formulas with content

plot(stm.model.12, "labels", topics = c(1:12), width = 1200, labeltype = "prob", n = 10, main = 'Top Topic Words - "Probability": STM Optimized Prevalence Model')

plot(stm.p.12, "labels", labeltype = "prob", width = 1200, topics = c(1:12), n = 10, main = 'Top Topic Words - "Probability": STM Prevalence Model')

# plot distribution of topic proportions -- the two prevalence models produce equivalent results

# `topics` must be named. plot.STM's signature is (x, type, n, topics, ...), so
# the third POSITIONAL argument is n, not topics: `plot(model, "hist", 1:12)`
# passed a length-12 vector as n, and labelTopics() then evaluated `if (n < 1)`
# on it. Under R < 4.2 that was a warning and the first element was used
# silently; from R 4.2 it is an error, which is how this surfaced.
# See CODE_REVIEW.md S2-7.

plot(stm.model.12, "hist", topics = c(1:12), main = "Frequency Distribution of Topics: STM Optimized Prevalence Model")

plot(stm.p.12, "hist", topics = c(1:12), main = "Frequency Distribution of Topics: STM Prevalence Model")
```
Use make.dt to create a data table for the model object that we can run queries against 

Combines the document-topic loadings (theta) with metadata to create a data.table object for easy querying.

```{r}
# create document table with and meta variables for stm_18

table.meta <- meta %>%
  select(doc_id, institution, gender, age, race)


t.12 <- make.dt(stm.p.12, meta = table.meta) %>%
  relocate(c(doc_id, institution, gender, age, race), .after = docnum)


# find 5 most associated documents for topic 1

t.12[docnum[order(Topic3, decreasing = TRUE)][1:10]]
```



Document topic proportions and essays - basic stm model

refs:

https://juliasilge.com/blog/sherlock-holmes-stm/
https://github.com/fracab/STMIndeed/blob/master/Indeed%20RJupyterNB2b.ipynb

```{r figure.height=20}
tidy_beta <- tidy(stm.p.12) # prob that each word is generated from each topic


tidy_gamma <- tidy(stm.p.12, matrix = "gamma") # prob that each doc is generated from each topic

tidy_gamma %>%
  filter(document == 1)

# associate docs, topic proportions, metadata

topic_prop12 <- make.dt(stm.p.12, meta)

# display data associations

head(topic_prop12)
```

Plot topic proportions by document

```{r}
# plot gammas

theta_plots <- tidy_gamma[tidy_gamma$document %in% c(1:9), ] # subset data

theta_plots %>% ggplot(aes(y = gamma, x = as.factor(topic), fill = as.factor(topic))) +
  geom_bar(stat = "identity", alpha = 0.8, show.legend = FALSE) +
  facet_wrap(~document, ncol = 3) +
  coord_flip() +
  labs(title = "Topic Proportions By Document (n=8210)", y = expression(theta), x = "Topic")
```

Perspective plot -- compares word probabilities across 2 topics

```{r}
# topic comparisons

plot(stm.p.12, "perspectives", topics = c(8, 12), n = 25, text.cex = 1)

plot(stm.p.12, "perspectives", topics = c(11, 3), n = 25, text.cex = 1)
```

Evaluate covariate main effects on topics -- 12 topics for this purpose. 


*Caution*

This process leverages the meta file to predict prevalence. A model specified for prevalence will produce somewhat different results from one specified for prevalence and content

```{r}
# covariate statistics
#
# Four estimateEffect() calls and four tidy-and-filter blocks stood here,
# identical but for the covariate. estimate_effects() and significant_effects()
# (R/covariate_effects.R) hold the shared arguments -- notably
# uncertainty = "Global", which propagates topic-proportion uncertainty into the
# standard errors and would narrow every interval reported if it were dropped
# from one copy.

covariate.preds <- estimate_effects(
  model = stm.p.12,
  metadata = meta,
  formulas = list(
    gender = 1:12 ~ gender,
    race = 1:12 ~ race,
    first_gen = 1:12 ~ first_gen,
    age = 1:12 ~ s(age)
  )
)

gender.pred <- covariate.preds$gender
race.pred <- covariate.preds$race
first.gen.pred <- covariate.preds$first_gen
age.pred <- covariate.preds$age


# tidy format - filter for significant effects

lapply(covariate.preds, significant_effects)

# summary format -- hash: topics with signf at 0.05

gp <- summary(gender.pred) # 1,2,3,5,7,8,9,11,12
rp <- summary(race.pred) # 2, 4,7,9
fgp <- summary(first.gen.pred) # 7,8,9,12
ag <- summary(age.pred) # 1, 3, 4, 5, 7, 8, 9, 10, 12
```
       

Plot effects - Gender: basic stm model

First Plot - Using first difference type estimate, where topic prevalence for a particular topic is contrasted for two groups

Second Plot - Topical content: plot the influence of covariates as a topical content covariate. A topical content variable allows for the vocabulary used to talk about a particular topic to vary. Note that type = perspective gives the highest probability words.

```{r}
# gender_pred and estimated_pred will produce the same plot

tidy(gender.pred)

plot_difference_effect(gender.pred,
  covariate = "gender", value1 = "F", value2 = "M",
  xlab = "More Male ... More Female",
  main = "Effect of Gender: K=12 Prevalence",
  xlim = c(-.06, .04), model = stm.p.12
)

```

A "gender comparison" perspectives plot stood here and has been **removed**. It
could not have produced what its title claimed, for three independent reasons
(`CODE_REVIEW.md` S2-8):

```r
plot(stm.p.12, "perspectives", topics = (1:12), n = 12, text.cex = 1,
     main = "Gender-Based Vocabulary: Test Anxiety")
```

- **`stm.p.12` has no content covariate.** It is the prevalence-only model — one
  beta group, no per-gender vocabulary. A `"perspectives"` plot on it cannot show
  gender-based word use, which is the thing the title promises.
- **`topics = 1:12` is not a valid perspectives argument.** The plot type
  contrasts one or two topics, not twelve. This is what made it error under
  R ≥ 4.2 rather than merely mislead.
- **The title names a single topic** — "Test Anxiety", topic 3 — contradicting
  the twelve topics passed.

The block immediately below does this correctly: it uses `stm.c.12`, the content
model, one topic per plot, with titles derived from the labels — and it already
includes topic 3. Nothing is lost by removing the broken line.
Plot differences in word content by gender 1,2,3,5,7,8,9,11,12

```{r}
# plot k = 12 model, content only

# Titles derive from topic_labels() rather than being retyped. Three of these
# had drifted from the labels they were meant to echo -- topic 7 used a hyphen
# where the label uses "&", topic 9 dropped a word, and topic 11 spelled
# "Applying" correctly while the label carried the "Appying" typo
# (CODE_REVIEW.md X-1). Deriving them means a label change propagates here
# automatically, which matters while the labels remain tentative.

for (k in c(1, 2, 3, 5, 7, 8, 9, 11, 12)) {
  plot(stm.c.12, "perspectives",
    topics = k, n = 25, text.cex = 1,
    main = paste0("Topic ", k, " = ", topic_labels(topics = k))
  )
}
```

Plot effects - race. Basic stm prevalence model. This section does not include all of the significant effects. See covariate regressions.

```{r}
tidy(race.pred)

# Guard the contrast values against the levels that actually exist. Before the
# S1-7 harmonisation, WGU wrote "Black" while the other institutions wrote
# "Black or African American", so the group occupied two levels and this plot
# contrasted only WGU's half of it. The levels are now merged, which means the
# literal "Black" no longer matches anything -- estimateEffect() would contrast
# against a level that is not there.
race_levels <- levels(as.factor(meta$race))
stopifnot(all(c("Black or African American", "Asian", "Latinx", "White") %in% race_levels))

for (group in c("Black or African American", "Asian", "Latinx")) {
  plot_difference_effect(race.pred,
    covariate = "race", value1 = group, value2 = "White",
    xlab = paste("More White ... More", group),
    main = "Effect of Race: K=12",
    xlim = c(-.05, .05), model = stm.p.12
  )
}
```


plot effects of first gen - basic stm model

```{r}
tidy(first.gen.pred)

# `Text.cex` (capital T) stood here and is not a graphical parameter, so it was
# ignored and R warned six times per plot. The shared arguments now live in
# plot_difference_effect(), where `cex` is spelled once.
plot_difference_effect(first.gen.pred,
  covariate = "first_gen", value1 = "FALSE", value2 = "TRUE",
  xlab = "More First Generation ... Less First Generation",
  main = "Effect of First Generation",
  xlim = c(-.04, .02), model = stm.p.12
)
```

Topic prevalence as a function of Age - basic stm prevalence model

Age is a statistically significant covariate for the following topics  1, 3, 4, 5, 7, 8, 9, 10, 12

```{r}
plot_continuous_effect(age.pred, "age", topics = 1:12, model = stm.p.12)
```

Plot age & gender interactions - basic stm prevalence model

```{r}
# build estimate effect formula

interact.signf <- estimateEffect(formula = c(1:12) ~ gender * age, stmobj = stm.p.12, metadata = meta, uncertainty = "Global")

# evaluate statistical significance of interaction

significant_effects(interact.signf, alpha = 0.1)

# summary format

gender.age <- summary(interact.signf) # 2,4,6

# plot the significant interactions of age and gender
#
# Three copies of the same triplet stood here -- male line, female line added
# over it, then a hand-placed legend -- differing only in topic number and y
# limits. The second call of each triplet has to omit `main` and `ylim` and pass
# `add = TRUE`, an asymmetry that drifts when copied, so it lives in
# plot_gender_age_interaction() (R/covariate_effects.R) instead.
#
# Y limits are per-topic: the curves occupy different ranges and a shared scale
# would flatten the smaller ones.

interaction.topics <- list(
  list(topic = 2, ylim = c(0, .1)),
  list(topic = 4, ylim = c(.04, .18)),
  list(topic = 6, ylim = c(0, .15))
)

for (spec in interaction.topics) {
  # The formula is built as text rather than written with `spec$topic` inline.
  # estimateEffect() evaluates the response term with the global environment as
  # its enclosure, so `spec` would be looked up there -- where it resolves to
  # readr::spec, a function, and fails with "object of type 'closure' is not
  # subsettable". Substituting the number first leaves nothing to look up.
  topic.effect <- estimateEffect(
    formula = stats::as.formula(paste0("c(", spec$topic, ") ~ gender * age")),
    stmobj = stm.p.12, metadata = meta, uncertainty = "Global"
  )

  plot_gender_age_interaction(
    topic.effect,
    model = interact.signf,
    topic = spec$topic,
    ylim = spec$ylim
  )
}
```
Create network plot for topics. Assign a cutoff threshold of 0.05

See: https://rdrr.io/cran/stm/src/R/topicCorr.R

```{r}
mod.out.corr <- topicCorr(stm.p.12, method = "simple", cutoff = .05)

plot(mod.out.corr, main = "K=12: Topic Network (P < 0.05)", vlabels = topic_labels(), vertex.label.cex = 0.75, label.color = "darkred", vertex.color = "lightblue")
```
